\documentclass[twoside,11pt,b5paper,twocolumn]{scrbook}
\usepackage{fontspec} % To use a beautiful font
\defaultfontfeatures{RawFeature={+hlig,+clig,+dlig,+cv11,+cv90,+calt,+ccmp,+swsh},%
  Numbers={Proportional,OldStyle},%
  SmallCapsFeatures={RawFeature={+smcp}},}


\usepackage[hidelinks]{hyperref} % check and put cross-references
\usepackage[british]{babel} % hyphenation
\usepackage{xcolor} % have colors
\usepackage{longtable}
\definecolor{marron}{RGB}{60,30,10}
\definecolor{darkblue}{RGB}{0,0,80}
\definecolor{lightblue}{RGB}{80,80,80}
\definecolor{darkgreen}{RGB}{0,80,0}
\definecolor{lightgreen}{RGB}{10,100,20}
\definecolor{darkgray}{RGB}{0,80,0}
\definecolor{darkred}{RGB}{80,0,0}
\definecolor{shadecolor}{rgb}{0.97,0.97,0.97}

\usepackage{wrapfig}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{graphicx}
\usepackage{scrlayer-scrpage} % have fancy headers and footers
\usepackage{lettrine} % For dopped capitals
\usepackage{dblfloatfix} % for specifying two-column table placement
\usepackage{fixltx2e} % for fixing two-column table placement
\usepackage[tmargin=2cm, bmargin=3cm,
lmargin=3cm, rmargin=1.5cm,
headheight=1.0cm,
headsep=0.4cm, footskip=1.5cm]{geometry}


\usepackage[final,stretch=10,protrusion=true,expansion=true]{microtype}
\microtypecontext{spacing=nonfrench}

\setmainfont[SmallCapsFont={EB Garamond}]{EB Garamond}
\setkomafont{disposition}{\rmfamily}

\setlength{\parskip}{1.3ex plus 0.2ex minus 0.2ex}


\usepackage{fourier-orns}

\newcommand{\ornamento}{\vspace{2em}\noindent \textcolor{darkgray}{\hrulefill~ \raisebox{-2.5pt}[10pt][10pt]{\leafright \decofourleft \decothreeleft \aldineright \decotwo \floweroneleft \decoone \floweroneright \decotwo \aldineleft\decothreeright \decofourright \leafleft} ~ \hrulefill \\ \vspace{2em}}}
\newcommand{\ornpar}{\noindent \textcolor{darkgray}{ \raisebox{-1.9pt}[10pt][10pt]{\leafright} \hrulefill \raisebox{-1.9pt}[10pt][10pt]{\leafright \decofourleft \decothreeleft \aldineright \decotwo \floweroneleft \decoone}}}
\newcommand{\ornimpar}{\textcolor{darkgray}{\raisebox{-1.9pt}[10pt][10pt]{\decoone \floweroneright \decotwo \aldineleft \decothreeright \decofourright \leafleft} \hrulefill \raisebox{-1.9pt}[10pt][10pt]{\leafleft}}}

\makeatletter
\def\headrule{{\color{darkgray}\raisebox{-2.1pt}[10pt][10pt]{\leafright} \hrulefill \raisebox{-2.1pt}[10pt][10pt]{~~~\decofourleft \decotwo\decofourright~~~} \hrulefill \raisebox{-2.1pt}[10pt][10pt]{ \leafleft}}}
\makeatother

\newcommand{\estcab}[1]{\textsc{\textcolor{marron}{#1}}}

\renewcommand{\chaptermark}[1]{}
\renewcommand{\sectionmark}[1]{}
\lohead{\estcab{\rightmark}}
\rohead{\estcab{\leftmark}}
\lehead{\estcab{\rightmark}}
\rehead{\estcab{\leftmark}}

\ofoot{}
\lofoot{\ornimpar \\ \large \hfill \textcolor{darkgray}{\leafNE ~~~ \textrm{\thepage}}}
\refoot{\ornpar \\ \large \textcolor{darkgray}{\textrm{\thepage} ~~~ \reflectbox{\leafNE}} \hfill}

\newcommand{\keyword}[1]{\textcolor{darkgreen}{#1}}
\renewcommand{\paragraph}[1]{\par\noindent\markboth{#1}{#1}\estcab{\keyword{#1}}\label{#1} }
\newcommand{\see}[1]{{\estcab{\hyperref[#1]{#1}}}}
\newcommand{\proverb}[1]{\par \textcolor{darkblue}{\itshape #1}}

\pagestyle{scrheadings}

\usepackage{chngcntr}
\counterwithout{figure}{chapter}
\counterwithout{table}{chapter}

\begin{document}

\begin{titlepage}
 \centering
 \vspace*{\baselineskip}
 \rule{\textwidth}{1.6pt}\vspace*{-\baselineskip}\vspace*{2pt}
 \rule{\textwidth}{0.4pt}\\[\baselineskip]
 
 {\Huge \itshape Encyclopædia Imperialys;}\\[0.4em]
 {\Large Or,\\[0.4em]}
 {\huge\scshape A Landskeeper's Compendium}\\
 \rule{\textwidth}{0.4pt}\vspace*{-\baselineskip}\vspace{3.2pt}
 \rule{\textwidth}{1.6pt}\\[\baselineskip]
 {\Large on Matters \scshape Magickal, Virtuous, Political {\normalfont and} Mundane,\\[1em]}
 {\itshape Compiled upon a New Plan, such that\\[0.5em]}
 {\large the different Arts and Practices are digested into distinct Essayes or Systems, including helpful Tables}
 
 {\itshape And\\[0.5em]}
 {\large All Technical Terms, \textit{\&c.} are explained as they occur \\[0.5em] \itshape in the Order of the Alphabet.}

 \vspace{0.8cm}
 {\bfseries Illustrated with enlightening Pictures.}
 
 \vfill
 
 Printed for Abbot James of Pickham,\\[0.4em]
 by Robyn Painter in {\itshape Pete’s Virtuous Printing-Office, T'King's Stoke}
 
 {\scshape Anno CCCLXXX}
\end{titlepage}
\begin{uppertitleback}{}
Contributions by James Appleseeder of Pickham, Abbot; t'late Peter Keeper, Cardinal and Landskeeper; Nicholas Reaper, Landskeeper; Martin Orchards, Landskeeper; t'late Annis Ramsbruck; Reinholz, Magistrate; and other members of t'Imperial Civil Service.

This book was written with t'intention to provide Wise and Vigilant ken, and to be an initial resource for any landskeeper looking to solve problems outside their field of expertise. Therefore, further contributions and any fundamental questions left unanswered are welcome.

All text, and all images marked \textit{*}, are published under civil service code \textit{cc-by-sa}, meaning that it will not be held against thee if thou findst this book helpful enough to reproduce any or all of it through other means.

Second edition, 379 YE.
\end{uppertitleback}
\setlength{\parindent}{1em}

\listoftables

\input{lemma}

\chapter{some useful rituals}
\label{appendix}
while imperial lore contains a great number of different rituals in all t'different realms, even a landskeeper not practicing t'magickal arts themself should be aware of some useful rituals, and at least roughly ken what is necessary to enact them.
\paragraph{strong ox, golden sun} summer \see{magnitude} 4. This ritual targets a farm which must already be enchanted with t'blessing of new spring ritual. T'character who controls t'target personal resource must be present throughout. This ritual completely replaces t'effect of blessing of new spring. T'target farm earns an additional 50 rings at t'summer solstice and t'autumn equinox. T'ritual ends at t'start of winter. This ritual is intended to be cast at t'spring equinox. If t'spell is cast later in t'year, then money that would have been gained in earlier seasons is lost. It is useless if performed after t'summer solstice. This ritual can affect additional farms in t'same territory. Each additional farm increases t'magnitude by 2.
\paragraph{blessing of new spring} spring \see{magnitude} 2 this ritual targets a farm. T'character who controls t'target personal resource must be present throughout. This ritual is an enchantment. A target may only be under one enchantment effect at a time. T'farm earns an additional 10 rings at t'spring equinox, t'summer solstice and t'autumn equinox. T'ritual ends at t'start of winter. This spell is intended to be cast at t'winter solstice. If t'spell is cast later in t'year, then money that would have been gained in earlier seasons is lost. It is useless if performed after t'summer solstice. This ritual can affect additional farms in t'same territory. Each additional farm increases t'magnitude by 1.
\paragraph{gathering t'harvest} autumn \see{magnitude} 15. This ritual targets a farm which must already be enchanted with t'strong ox, golden sun ritual. T'character who controls t'target personal resource must be present throughout. This ritual completely replaces t'effect of strong ox, golden sun. T'farm earns an additional 400 rings at t'autumn equinox. T'ritual ends at t'start of winter. This ritual is intended to be cast at t'summer solstice. If t'spell is cast earlier in t'year, then money that would have been gained from strong ox, golden sun or blessing of new spring is lost. T'effect lasts until t'start of t'next summit. If t'owner of t'resource does not attend t'next event, then t'additional production provided by t'resource is still added to that character's inventory. This ritual can affect additional farms in t'same territory. Each additional farm increases t'magnitude by 12.
\paragraph{bright lantern of ophis} day \see{magnitude} 6 t'ritual reveals information about an enchantment, \see{curse} or other magickal effect. It is most often used on a character or item that is present. It can also be used on a special effect that is anchored to an area. It determines t'realm and magnitude of t'effect; it determines what t'effect does, and provides details of how it works; it reveals any remaining duration; it reveals any conditional effects, or any special methods that exist for removing t'effect; it may provide information about where t'magickal effect has come from (a ritual or t'supernatural abilities of an \see{eternal}, for example). you may increase t'magnitude of t'ritual to penetrate more powerful shrouds or masks.
\paragraph{circle of gold} autumn \see{magnitude} 9 this ritual targets up to five characters from t'same band. Each character must be present throughout. T'target characters gain t'ability to use stay with me once without needing to ken t'skill or spend any hero points; however, they can only use t'ability on another character who was also a target of this ritual. They feel a desire to stick together, whether on t'battlefield or off it. They feel a strong urge to defend t'other targets of t'ritual, whether from physical harm or from insults. T'effect lasts until t'end of t'next \see{battle}, skirmish or quest t'character participates in; or until t'end of t'current event, whichever is sooner. This ritual can affect additional characters from t'same band. Every two additional characters increases t'magnitude by 3. Additional characters must be present throughout. Any caster who has mastered t'ritual may choose to substitute weltsilver for crystal mana when contributing to it. Every 2 ingots of weltsilver spent counts as 1 crystal mana when contributing to t'ritual.

\chapter{exemplary stories from t'Marches}
\label{stories}
\input{stories}
\end{document}
%%% Local Variables: 
%%% coding: utf-8
%%% mode: latex
%%% TeX-engine: xetex
%%% TeX-master: "encyclopedia"
%%% End: 
